Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-07 paper.tex
more fixes

\Omit{ 
\textbf{Use case:}
A {\em Use case} is a set of scenarios that satisfy 
a particular goal. A use case completes successfully 
when that goal is satisfied. A complete set of use cases 
defines all the behaviors required of the system. For example, 
a use case in case of UART  may be to transmit 
the data through the serial port. A scenario is an 
instance of a use case. 
}
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{st.pspdftex}}
\caption{Scenario and Firmware Transaction
\label{fig:st}}
\end{figure}

@@

the values of predicates, $'UART\_MC, 'UART\_IE, 'UART\_CT$.  Assuming that
$'UART\_MC$ holds true, the execution proceeds to $t_6$.  During the

@@

\textit{software netlist}~\cite{mtk2016,mskm2016,mkm2015} following synthesis 

@@

models from RTL description, primarily targeted for word-level formal verification.  
To the best of our knowledge, this is the first attempt to demonstrate the 
efficacy of such a translation in the context of hardware/software co-verification. 

@@

Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
in UART . The FW CFG is shown in the left and the HW RTL code snippet 
is shown in the right. We abuse notations and 
represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
for illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
The signal $irq\_o$ is  triggered when transmitter buffer is 
{\em EMPTY} or receiver buffer is {\em FULL}. 
$\mathcal{HT}$ also produces interrupt status by writing to the 
memory mapped register, $UART\_IS$, which is consumed by 
$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
in state $s_6$ which is consumed by $\mathcal{HT}$.  
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
\caption{Producer Consumer Interactions Pattern
\label{fig:interleaving1}}
\end{figure}
%

Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
interacting HW transactions $(\mathcal{HT})$ from Figure~\ref{fig:interleaving1}. 
The description above the arrows 
in column 1 shows the events in $\mathcal{FT}$ and the letter below the
arrows denotes the event type, producer $(\mathcal{P})$ or consumer 
$(\mathcal{C})$. Arrows with empty description below denotes reading of interface
variables or local variables in $\mathcal{FT}$.  Arrows with no description
simply denotes control-flow join.  The entries in the right column of
Table~\ref{transaction} shows the corresponding transactions in HW.  We 
denote a transaction in HW module with the name of the module,
transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
the top UART module ($uart\_top$).
%
\begin{table}
\begin{center}
{
 \scriptsize
\begin{tabular}{|c|c|c|}
\hline
  Firmware & Hardware  \\
  Transaction ($\mathcal{ST}$) & Transaction ($\mathcal{HT}$) \\ 
\cline{1-2}
   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
   \xrightarrow[]{status == 0x0c} s_6 \xrightarrow[\mathcal{P}]{outb()} s_9 \rightarrow
   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
   \\ 
   & $s_6 \xrightarrow[]{outb()} s_9\;\; uart\_{tx}$ \\  \hline

@@

\textbf{Step 3: Co-verification Model}
%
An unified co-verification model is constructed through appropriate composition of 
FW and its interacting HW transaction.  This is done by instrumenting the 
software netlist model of HW RTL inside the FW transaction at every invocation 
of the $next\_timeframe()$ primitive in interface functions.  Recall that a
call to $next\_timeframe()$ is used to advance the HW clock by one cycle.  A call
to the software netlist emulates the effect of one clock period in the RTL 
model. That is, the configuration of state holding elements (registers) and combinational 
elements (wires) are uniform in software netlist and RTL model after every invocation of 
$next\_timeframe()$.  Furthermore, a software
netlist is a sequential model of HW RTL which is represented in C.  Thus, the
composition leads to a single-threaded sequential co-verification model in C.  
%
We now formally define our co-verification model, denoted by 
$\mathcal{M}_{seq}$.
%
\[ 
\begin{array}[t]{@{}lll}
  \mathcal{M}_{seq} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
\end{array}
\]
%
Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
over variables $Var$ of $\mathcal{M}_{seq}$ such that $(exp \in Exp)$ and 
$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
conditional, sequential concatenation or a loop.
$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
procedure of $\mathcal{SN}$, which is also the top level 
module of the HW RTL, since the translation from RTL to software preserves
the module hierarchy.  The interface variables $\{Var\_1,\dots,Var\_n\}$ 
(input, output and inout ports) are declared inside the 
FW to communicate with $\mathcal{SN}$.  Figure~\ref{compose} shows the 
composition of $\mathcal{SN}$ and FW transaction for UART.
%
\begin{figure}[t]
\scalebox{.50}{\import{figures/}{compose.pspdftex}}
  \caption{Composition of FW and HW transactions}
\label{compose}
\end{figure}

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{\small Monolithic HW/SW Co-verification Flow in \hwcbmcv}
\label{fig:conventional}
\end{center}
\end{figure}
%
\textbf{Step 1: Co-verification Model}
%
Figure~\ref{fig:conventional} illustrates the monolithic approach to HW/SW
co-veri\-fi\-cation, as implemented in \hwcbmcv.  
%\hwcbmcv is the only open-source
%formal co-verification tool that supports Verilog RTL (System Verilog 2009
%standard) and C/C++ firmware.  
In contrast to path-based approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  A bit-level netlist is represented 
in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
in format that resembles SMT-LIB2 standards~\footnote{http://smtlib.cs.uiowa.edu/}.  
The bottom flow illustrates the translation of C program 
into static single assignment (SSA) form. 
Synthesizing netlist from RTL is a standard technique which is widely 
used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
Similarly, translating a C program into an SSA representation is a 
standard technique which is widely used in 
software verification tools, such as CBMC~\cite{cbmc.tacas:2004}. 
\hwcbmcv generates a monolithic co-verification model from AIG and SSA through 
in-tandem symbolic execution of HW and FW components.

@@

%-------------------------------------------------------------------------------
\subsection{Component level Property}
%-------------------------------------------------------------------------------
A {\em component level} property ($\psi_{c}$) is defined purely at the 
level of individual components of a co-design system. Recall that a component 
may be a HW model, a SW model or an interface model which contains only the 
interface logic.  A component-level property captures the design intent of a 
component in terms of its input/output behaviors.  This type of property 
is useful in a co-design environment for verifying individual components.   
Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
(ports) or variables of a particular component.  Figure~\ref{figure:component} 
shows an example of component level property for the UART HW only.  The 
System Verilog Assertion (SVA) is shown on the left and the equivalent 
monitor in C is shown on the right.  
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
System Verilog Assertions  & Monitor (in C)
\\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
P3: assert property 
 (@(posedge clk) 
 ack == 1|-> 
 (valid == 1 && 
 ##2 empty == 0)); 
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
bool monitor_P3() {
 assert(!ack || valid);
 next_timeframe();
 next_timeframe();
 assert(empty==0); }
\end{lstlisting} \\
\hline
\end{tabular}
\caption{Component level property as monitor (in C)}
\label{figure:component}
\end{figure}
%
%-------------------------------------------------------------------------------
\subsection{Debugging Using Counterexample Trace}
%-------------------------------------------------------------------------------
A failure of co-design property implies a fault in HW or a defective FW 
or bug in the interface functions.  Hence, an important feature of a
co-verification tool is its ability to produce a counterexample trace 
in order to localize the bug.  \hwcbmcv generates a counterexample
trace in value change dump (vcd) format that contains concrete assignments to FW
variables, interface signals and HW RTL signals up to a given bound. Whereas, a
counterexample trace in \verifox is a bounded path in the sequential co-verification
model that contains a scenario and its corresponding HW and FW transactions. 
%
%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART  and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  The performance of bit-level 
and word-level flow in \hwcbmcv are similar. So, we only report bit-level 
results for \hwcbmcv.  MiniSAT-2.2.0~\cite{DBLP:conf/sat/EenB05} was used 
as underlying SAT solver with \hwcbmcv and \verifox.  The focus of our 
experiments is to compare the performance of path-based technique in \verifox 
with monolithic BMC approach in \hwcbmcv for verification of UART and SoC design.  
\\ 
%

@@

The result in Table~\ref{table:SoC} shows that \verifox is approximately
$2\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
the speedup is $6\times$ for \verifox over \hwcbmcv. \\ 
\textbf{\emph{Monolithic versus Path-based:}}
The reason for better scalability of \verifox compared to 
\hwcbmcv is attributed to the path-based exploration of a 
sequential co-verification model using eager path pruning and 
incremental SAT solving to automatically mine relevant scenario/transaction
pairs.  In the case of SoC, the FW exercises only the micro-controller 
and transfer sequence of bytes to the XRAM port bypassing peripherals 
connected to other ports such as hardware accelerator.  
This scenario allows path-based exploration techniques to prune the logic for
accelerator and thereby generate only relevant scenario/transaction pairs.  It 
is important to note that forward symbolic execution without these optimizations 
timeout for all the benchmarks.

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution by generating relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between participating 
threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
interaction pattern is prevalent in many practical 
co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.

>>>>

\Omit{ 
\textbf{Use case:}
A {\em Use case} is a set of scenarios that satisfy 
a particular goal. A use case completes successfully 
when that goal is satisfied. A complete set of use cases 
defines all the behaviors required of the system. For example, 
a use case in case of UART  may be to transmit 
the data through the serial port. A scenario is an 
instance of a use case. 
}
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{st.pspdftex}}
  \caption{Scenario (left) and Firmware Transactions (right)
\label{fig:st}}
\end{figure}

@@

the values of predicates, $UART\_MC, UART\_IE, UART\_CT$.  Assuming that
$UART\_MC$ holds true, the execution proceeds to $t_6$.  During the

@@

\textit{software netlist}~\cite{mtk2016} following synthesis 

@@

models from RTL description, primarily targeted for formal 
verification~\cite{mtk2016,mskm2016,mkm2015}.  To the best of our knowledge, 
this is the first attempt to demonstrate the efficacy of such a 
translation in the context of hardware/software co-verification. 

@@

Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
in UART. The FW CFG is shown in the left and the HW RTL code snippet 
is shown in the right. We abuse notations and 
represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
for illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
The signal $irq\_o$ is  triggered when transmitter buffer is 
{\em EMPTY} or receiver buffer is {\em FULL}. 
$\mathcal{HT}$ also produces interrupt status by writing to the 
memory mapped register, $UART\_IS$, which is consumed by 
$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
in state $s_6$ which is consumed by $\mathcal{HT}$.  
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
\caption{Producer Consumer Interactions Pattern
\label{fig:interleaving1}}
\end{figure}
%

Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
interacting HW transactions $(\mathcal{HT})$ from Figure~\ref{fig:interleaving1}. 
The description above the arrows 
in column 1 shows the events in $\mathcal{FT}$ and the letter below the
arrows denotes the event type, producer $(\mathcal{P})$ or consumer 
$(\mathcal{C})$. Arrows with empty description below denotes reading of interface
signals or local FW variables in $\mathcal{FT}$.  Arrows with no description
simply denotes control-flow join.  The entries in the right column of
Table~\ref{transaction} shows the corresponding transactions in HW.  We 
denote a transaction in HW with the name of the module, transmitter module 
in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or the top 
UART module ($uart\_top$).
%
\begin{table}
\begin{center}
{
 \scriptsize
\begin{tabular}{|c|c|c|}
\hline
  Firmware & Hardware  \\
  Transaction ($\mathcal{ST}$) & Transaction ($\mathcal{HT}$) \\ 
\cline{1-2}
   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
   \xrightarrow[]{status == 0x0c} s_6 \xrightarrow[\mathcal{P}]{outb()} s_9 \rightarrow
   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
   \\ 
   & $s_6 \xrightarrow[]{outb()} s_9\;\; uart\_{tx}$ \\  \hline

@@

\textbf{Step 3: Co-verification Model}
%
An unified co-verification model is constructed through appropriate composition of 
FW and its interacting HW transaction.  This is done by instrumenting the 
software netlist model of HW RTL inside the FW transaction at every invocation 
of the $next\_timeframe()$ primitive in interface functions.  Recall that a
call to $next\_timeframe()$ is used to advance the HW clock by one cycle.  A call
to the software netlist emulates the effect of one clock period in the RTL 
model. That is, the configuration of state holding elements (registers) and combinational 
elements (wires) are uniform in software netlist and RTL model after every invocation of 
$next\_timeframe()$.  Furthermore, a software
netlist is a sequential model of HW RTL which is represented in C.  Thus, the
composition leads to a single-threaded sequential co-verification model in C.  
%
We now formally define our co-verification model, denoted by 
$\mathcal{M}_{seq}$.
%
\[ 
\begin{array}[t]{@{}lll}
  \mathcal{M}_{seq} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
\end{array}
\]
%
Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
over variables $Var$ of $\mathcal{M}_{seq}$ such that $(exp \in Exp)$ and 
$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
conditional, sequential concatenation or a loop.
$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
procedure of $\mathcal{SN}$, which is also the top level 
module of the HW RTL, since the translation from RTL to software preserves
the module hierarchy.  The interface signals $\{Var\_1,\dots,Var\_n\}$ 
(input, output and inout ports) are declared inside the 
FW to communicate with $\mathcal{SN}$.  Figure~\ref{compose} shows the 
composition of $\mathcal{SN}$ and FW transaction for UART.
%
\begin{figure}[t]
\scalebox{.50}{\import{figures/}{compose.pspdftex}}
  \caption{Composition of FW and HW transactions}
\label{compose}
\end{figure}

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{\small Monolithic HW/SW Co-verification Flow in \hwcbmcv}
\label{fig:conventional}
\end{center}
\end{figure}
%
\textbf{Step 1: Co-verification Model}
%
Figure~\ref{fig:conventional} illustrates the monolithic approach to HW/SW
co-veri\-fi\-cation, as implemented in \hwcbmcv.  
%\hwcbmcv is the only open-source
%formal co-verification tool that supports Verilog RTL (System Verilog 2009
%standard) and C/C++ firmware.  
In contrast to path-based approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  A bit-level netlist is represented 
in And Inverter Graph (AIG) format.  Whereas, a word-level netlist is represented 
in format that resembles SMT-LIB2 standards~\footnote{http://smtlib.cs.uiowa.edu/}.  
The bottom flow illustrates the translation of C program 
into static single assignment (SSA) form. 
Synthesizing netlist from RTL is a standard technique which is widely 
used in hardware model checkers~\cite{DBLP:journals/tse/Clarke76}.
Similarly, translating a C program into an SSA representation is a 
standard technique which is widely used in 
software verification tools, such as CBMC~\cite{cbmc.tacas:2004}. 
\hwcbmcv generates a monolithic co-verification model from AIG and SSA through 
in-tandem symbolic execution of HW and FW models.

@@

%-------------------------------------------------------------------------------
\subsection{Component level Property}
%-------------------------------------------------------------------------------
A {\em component level} property ($\psi_{c}$) is defined purely at the 
level of individual components of a co-design. Recall that a component 
may be a HW model, a SW model or an interface model which contains only the 
interface logic.  A component-level property captures the design intent of a 
component in terms of its input/output behaviors.  This type of property 
is useful in a co-design environment for verifying individual components.   
Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
(ports) or variables of a particular component.  Figure~\ref{figure:component} 
shows an example of component level property for the UART HW only.  The 
System Verilog Assertion (SVA) is shown on the left and the equivalent 
monitor in C is shown on the right.  
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
System Verilog Assertions  & Monitor (in C)
\\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
P3: assert property 
 (@(posedge clk) 
 ack == 1|-> 
 (valid == 1 && 
 ##2 empty == 0)); 
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
bool monitor_P3() {
 assert(!ack || valid);
 next_timeframe();
 next_timeframe();
 assert(empty==0); }
\end{lstlisting} \\
\hline
\end{tabular}
\caption{Component level property as monitor (in C)}
\label{figure:component}
\end{figure}
%
%-------------------------------------------------------------------------------
\subsection{Debugging Using Counterexample Trace}
%-------------------------------------------------------------------------------
A failure of co-design property implies a fault in HW or a defective FW 
or bug in the interface functions.  Hence, an important feature of a
co-verification tool is its ability to produce a counterexample trace 
in order to localize the bug.  \hwcbmcv generates a counterexample
trace in value change dump (vcd) format that contains concrete assignments to FW
variables, interface signals and HW RTL signals up to a given bound. Whereas, a
counterexample trace in \verifox is a bounded path in the sequential co-verification
model that contains a scenario and its corresponding HW and FW transactions. 
%
%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART  and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  The performance of bit-level 
and word-level flow in \hwcbmcv are similar. So, we only report bit-level 
results for \hwcbmcv.  MiniSAT-2.2.0~\cite{DBLP:conf/sat/EenB05} was used 
as underlying SAT solver with \hwcbmcv and \verifox.  The focus of our 
experiments is to compare the performance of path-based technique in \verifox 
with monolithic BMC approach in \hwcbmcv for verification of UART and SoC design.  
\\ 
%

@@

The result in Table~\ref{table:SoC} shows that \verifox is approximately
$2\times$ faster than \hwcbmcv for proving safety.  For detecting bugs, 
the speedup is $6\times$ for \verifox over \hwcbmcv. \\ 
\textbf{\emph{Monolithic versus Path-based:}}
The reason for better scalability of \verifox compared to 
\hwcbmcv is attributed to the path-based exploration of the 
sequential co-verification model using eager path pruning and 
incremental SAT solving to automatically mine relevant scenario/transaction
pairs.  In the case of SoC scenario (data\_transfer), the FW exercises 
only the micro-controller and transfer sequence of bytes to the XRAM port 
bypassing peripherals connected to other ports such as hardware accelerator.  
This scenario allows path-based exploration techniques to prune the logic for
accelerator and thereby generate only relevant scenario/transaction pairs.  It 
is important to note that forward symbolic execution without these optimizations 
timeout for all the benchmarks.

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  Such interaction pattern 
is prevalent in many practical co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}. 
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution by generating relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between participating 
threads in an efficient manner.
